Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-24 latex/afm-cs-main.tex
Add headshots.

\begin{IEEEbiography}{Roger A. Braker} is so happy that all this is almost done.

@@

\begin{IEEEbiography}[{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{yufan.JPG}}]{Yufan Luo}
received dual B.S. degrees in automation and in management science from Zhejiang University, Zhejiang, China, in 2011, an M.S. degree in industrial and operations engineering from the University of Michigan, Ann Arbor, MI, USA, in 2012, and a Ph.D. degree in systems engineering from Boston University in 2019. He is currently with Juniper Networks, Sunnyvale, CA.

@@

\begin{IEEEbiography}{Lucy Y. Pao} is probably not so happy that Arnold's almost done.

@@

\begin{IEEEbiography}[{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{SeanAndersson_IEEE.jpg}}]{Sean B. Andersson}
received the B.S. degree in engineering and applied physics from Cornell University, Ithaca, NY, USA, in 1994, the M.S. degree in mechanical engineering from Stanford University, Stanford, CA, USA, in 1995, and the Ph.D. degree in electrical and computer engineering from the University of Maryland, College Park, MD, USA, in 2003. He has worked at AlliedSignal Aerospace and Aerovironment, Inc. and is currently an Associate Professor of mechanical engineering and of systems engineering with Boston University, Boston, MA, USA. His research interests include systems and control theory with applications in scanning probe microscopy, dynamics in molecular systems, and robotics. He received an NSF CAREER award in 2009, is a senior member of the IEEE, and was an associate editor for the IEEE Transactions on Automatic Control (2014-2018) and for the SIAM Journal on Control and Optimization (2013-2018).
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}
  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/braker_headshot.jpg}}]
  {Roger A. Braker} is so happy that all this is almost done.

@@

\begin{IEEEbiography}
  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/yufan.JPG}}]
  {Yufan Luo}
received dual B.S. degrees in automation and in management science from Zhejiang University, Zhejiang, China, in 2011, an M.S. degree in industrial and operations engineering from the University of Michigan, Ann Arbor, MI, USA, in 2012, and a Ph.D. degree in systems engineering from Boston University in 2019. He is currently with Juniper Networks, Sunnyvale, CA.

@@

\begin{IEEEbiography}
  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/pao_headshot.jpg}}]
  {Lucy Y. Pao} is probably not so happy that Arnold's almost done.

@@

\begin{IEEEbiography}
  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/SeanAndersson_IEEE.jpg}}]
  {Sean B. Andersson}
received the B.S. degree in engineering and applied physics from Cornell University, Ithaca, NY, USA, in 1994, the M.S. degree in mechanical engineering from Stanford University, Stanford, CA, USA, in 1995, and the Ph.D. degree in electrical and computer engineering from the University of Maryland, College Park, MD, USA, in 2003. He has worked at AlliedSignal Aerospace and Aerovironment, Inc. and is currently an Associate Professor of mechanical engineering and of systems engineering with Boston University, Boston, MA, USA. His research interests include systems and control theory with applications in scanning probe microscopy, dynamics in molecular systems, and robotics. He received an NSF CAREER award in 2009, is a senior member of the IEEE, and was an associate editor for the IEEE Transactions on Automatic Control (2014-2018) and for the SIAM Journal on Control and Optimization (2013-2018).
\end{IEEEbiography}
